Contrastive Optimization -- Preliminaries

### 2024-10-30 paper/main.tex
added models, updated evals, minor paper tweaks

\newtheorem{theorem}{Proposition}
\newtheorem{corollary}{Corollary}[theorem]

@@

For the multiclass case, our setup now considers a set of classes $c$; $c_t$ is our target class, and $c_{t'}$ consists of a sampled non-target class. The definition for multiclass contrastive activation maps now results in a set of activation maps, defined as follows:
\begin{gather}
	\tilde{\mathcal{\bm{A}}}^{\text{contrastive}}_{(c_t, c_{t'})} := \left\{\tilde{\mathcal{\bm{A}}}_{c_t}^{\text{HiResCAM}} - \tilde{\mathcal{\bm{A}}}_{c_{t'}}^{\text{HiResCAM}}\right\}^{|C|-1}_{c_{t'} \in c - c_t}
\end{gather}
This is a generalization of the binary case, as the same formula applied to a binary classification challenge returns a set of contrastive maps containing a single element.

>>>>

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

@@

We can define ContrastiveCAMs as a generalization of the binary case.

\begin{definition}
	Given a set of classes $C$ with $c_t$ being the target class and $c_{t'}$ being a sampled non-target class, we define ContrastiveCAMs as follows:
	\begin{gather}
		\tilde{\mathcal{\bm{A}}}^{\text{contrastive}}_{(c_t, c_{t'})} := \left\{\tilde{\mathcal{\bm{A}}}_{c_t}^{\text{HiResCAM}} - \tilde{\mathcal{\bm{A}}}_{c_{t'}}^{\text{HiResCAM}}\right\}^{|C|-1}_{c_{t'} \in c \setminus c_t}
	\end{gather}
\end{definition}

This enables us to evaluate ContrastiveCAMs in the multiclass setting. This is trivially a generalization of the previous case, as the same formulation applied to a binary classification task returns a set of contrastive maps containing a single element.
